International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-17 paper/3_sim.tex
notes

We utilize a simulation study to highlight the utility of AME as an inferential tool for dyadic analysis. We are particularly interested in whether AME can provide unbiased and well calibrated estimates of coefficient parameters in the presence of unobserved network dependencies. Specifically, we are concerned with conducting inference on a regression parameter $\beta$ of a linear model for a network in the case where there is an omitted variable. Say that the true data-generating process for a particular $Y$ is given by:

$y_{i,j} \sim  \mu + \beta x_{i,j} + \gamma w_{i,j} + \epsilon_{i,j} $

@@

\begin{itemize}
	\item A naive regression model assuming independent errors; 
	\item A latent factor model; 
	\item An ``oracle'' regression model that includes both $x_{i,j}=x_i x_j$ and $w_{i,j}=w_i w_j$. 
\end{itemize}

We make these comparisons in the context of a linear network outcome with the AME probit regression model described in the previous section.

>>>>

We utilize a simulation study to highlight the utility of AME as an inferential tool for dyadic analysis. The goal of the simulation is to assess how well AME can provide unbiased and well calibrated estimates of coefficient parameters in the presence of unobserved network dependencies. [link to previous discussion] Specifically, we are concerned with conducting inference on a regression parameter $\beta$ of a linear model for a network in the case where there is an omitted variable. Say that the true data-generating process for a particular $Y$ is given by:

\begin{align*}
	y_{i,j} \sim  \mu + \beta x_{i,j} + \gamma w_{i,j} + \epsilon_{i,j} \\
	\label{eqn:sim}
\end{align*}

@@

\begin{itemize}
	\item the standard IR approach assuming independent errors; 
	\item the AME approach outlined in the previous section;
	\item and an ``oracle'' regression model that includes both $x_{i,j}$ and $w_{i,j}$. 
\end{itemize}

We run this simulation
